Presentation Title

### 2017-08-09 paper/s2-related.tex
Write/fix paper

\section{Background and Related Work}
% give background on ACS
% give background on TrustChain?

\subsection{Background on asynchronous subset consensus}
\label{sec:acs-background}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Totality:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resilience when compared to other consensus algorithms.
For instance, Hyperledger and Tendermint uses a variant of Practical Byzantine Fault Tolerance (PBFT)~\cite{castro1999practical} as their consensus algorithm.
In PBFT, a leader is elected, if the leader is malicious but follows the protocol, then it can selectively filter transactions.
In contrast, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.
Thus, if some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
For a detailed description of ACS, we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.
To understand the remainder of this work, the knowledge of~\Cref{def:acs} is sufficient.

The main drawback with ACS and also Byzantine consensus algorithms is the high message complexity.
Typically, such protocols have a message complexity of $O(n^2)$, where $n$ is the number of parties.
Hence, it may work with a small number of nodes,
but it is infeasible for blockchain systems where thousands of nodes are involved.

% The literature on Byzantine consensus and atomic broadcast is rich, some noteable ones include TODO.
% Thus in the ETC consensus protocol, we assume there exist an "off-the-shelf" Byzantine consensus algorithm which we can use
% (in our implementation we use HoneyBadgerBFT and motivate our choice in TODO).

% In our case, every node do not propose some arbitrary data, but a set of CP blocks.
% Thus the result of the consensus is the set union of all the legitimate proposals.

@@

Off-chain transaction systems are implemented using multi-signature addresses~\cite{bitcoinmultisig} and hashed time-locked Bitcoin contracts~\cite{bitcointimelock}.
In the simplest case, 
if two parties wish to make transactions,
they open a payment channel in the form of a multi-signature Bitcoin address (for two parties it would be a 2-of-2 signature address).
Each of the party must also deposit some Bitcoins in the multi-signature address,
this is called the opening transaction.
Both parties keep the channel state which is not broadcasted to the network.
The state is updated when the two parties make new transactions.
The protocol disincentivises the parties from broadcasting old channel states.
If this occurs, the counterparty can drain all the Bitcoins in the channel.
To close the channel, the parties simply broadcast the latest net settlement to the Bitcoin network,
this is called the closing transaction.
Effectively, only two transactions need to be broadcasted to the Bitcoin network---the opening and the closing transaction,
even if the two parties made thousands or millions of transactions in between.
The two-party scheme can be extended to a network of channels,
which allows two parties to make off-chain transactions without an open channel as long as they are connected by nodes that do.

The advantage of such systems is that they act as add-ons to Bitcoin wish already has a large number of users.
Thus, if enough of the network wish for it (by setting a new block version),
then a large number of users will instantly benefit from it.
Some implementations already exist\footnote{For example \url{https://github.com/lightningnetwork/lnd}.},
but at the time of writing SegWit is not activated yet which is a prerequisite for Lightning Network.

On the other hand, off-chain transactions also suffer from the problem of Bitcoin.
Namely, proof-of-work consumes an unreasonable amount of power.
Further, payment channels complicate user experience.
As we mentioned earlier, each node must deposit some Bitcoins into a multi-signature account.
The users must pick a suitable amount.
If the deposit is too low it would not allow large transactions.
If the deposit is too high the user is locked out of much of its Bitcoins for use outside of the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Payment channel, in theory, solves the scalability problem of early blockchain systems,
but to the best of our knowledge, its exact scalability characteristics are not investigated.

@@

\subsection{Blockchain without global consensus}

Tangle~\cite{tangle}, Corda~\cite{corda} and the original TrustChain~\cite{multichain} do not use global consensus at all.
In this scheme, every node has their own chain.
Transactions between nodes are recorded on their respective chains.
This effectively results in a directed acyclic graph.
By avoiding global consensus, this approach achieves extremely desirable scalability properties similar to BitTorrent~\cite{cohen2003incentives}.

On the other hand, the application and security are limited.
A malicious node can easily lie to other nodes regarding its own chain by simply presenting one version of reality to a set of nodes and another version to a different set.
Thus the network will have a conflicting view on the state of the malicious node.
Applications such as digital cash can not be implemented on top of such systems because consistency is needed in solving the double spending problem.

>>>>

\section{Background and Related Work}

Making early blockchain systems scalable has received much attention from both the academia and the industry in recent years.
This section gives an mini taxonomy of the state-of-the-art, categorised by the scalability approach.
At the end of this section,
we describe the important--asynchronous subset consensus (ACS),
which is the key building block of our work.

@@

Off-chain transactions promises significant scalability improvements, but it suffer from the problem of Bitcoin.
Namely, proof-of-work consumes an unreasonable amount of power.
Further, payment channels complicate user experience.
As we mentioned earlier, each node must deposit some Bitcoins into a multi-signature account.
The users must pick a suitable amount.
If the deposit is too low it would not allow large transactions.
If the deposit is too high the user is locked out of much of its Bitcoins for use outside of the channel.
In addition, the user must proactively check whether the counterparty has broadcasted an old channel state so that the user does not lose Bitcoins.
Payment channel, in theory, solves the scalability problem of early blockchain systems,
but to the best of our knowledge, its exact scalability characteristics are not investigated.

@@

\subsection{Asynchronous subset consensus}
\label{sec:acs-background}

There are $n$ nodes, of which at most $t$ might experience Byzantine fault.
Node $i$ starts with a non-empty set of input values $C_i$.
The nodes must decide an output $C$, satisfying the following.
\begin{enumerate}
    \item \emph{Agreement:}
        If a correct node outputs $C$, then every node outputs $C$.
    \item \emph{Validity:}
        If any correct node outputs a set $C$,
        then $|C| \ge n - t$ and $C$ contains the input of at least $n - 2t$ nodes.
    \item \emph{Termination:}
        If $n - t$ nodes receive an input, then all correct nodes produce an output.
\end{enumerate}
\end{definition}

ACS has the nice property of censorship resilience when compared to other consensus algorithms.
For instance, a leader is elected in PBFT~\cite{castro1999practical},
if the leader is malicious but follows the protocol, then it can selectively filter transactions.
In contrast, every party in ACS are involved in the proposal phase,
and it guarantees that if $n - 2t$ parties propose the same transaction, then it must be in the agreed output.
Thus, if some value is submitted to at least $n - 2t$ nodes, it is guaranteed to be in the consensus result.
The total communication complexity of ACS is $O(n^2 |v| + \lambda n^3 \log(n))$,
where $n$ is the number of nodes, $|v|$ is the message size and $\lambda$ is the security parameter.
For a detailed description of ACS, we refer to the HoneyBadgerBFT work~\cite{miller2016honey}.

### 2017-08-09 paper/s3-system.tex
Write/fix paper

@@

This section and the ones following it give a technical treatment of what the content in System overview.
For notational clarity, we use the following convention (adapted from~\cite{miller2016honey}) for most of this work.
\begin{itemize}
\item Lower case (e.g. $x$) denotes a scalar object or a tuple.
\item Upper case (e.g. $X$) denotes a set or a constant.
\item Sans serif (e.g. $\textsf{fn}(\cdot)$) denotes a function.
\item Monospace (e.g. $\texttt{ack}$) denotes message type.
\end{itemize}
Further, we use $a || b$ to denote concatenation of the binary representations of $a$ and $b$.

We assume purely asynchronous channels with eventual delivery.
Thus in no stage of our protocol do we make timing assumptions.
The adversary has full control of the delivery schedule and the message ordering of all messages.
But they are not allowed to drop messages except for their own\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
}.

We assume there exists a Public Key Infrastructure (PKI), and nodes are identified by their unique and permanent public key.
Finally, we use the random oracle (RO) model, i.e. calls to the random oracle are denoted by $\textsf{H}: \{0, 1\}^* \rightarrow \{0, 1\}^\lambda$,
where $\{0, 1\}^*$ denotes the space of finite binary strings and $\lambda$ is the security parameter.
Under the RO model, the probability of successfully computing the inverse of the hash function is negligible with respect to $\lambda$~\cite{bellare1993random}.

@@

Our consensus protocol runs in rounds as discussed in \Cref{sec:system-overview}.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e. $\C_r = \langle r, C \rangle$,
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

@@

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \texttt{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \texttt{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Note that $c_{u, a}$ is the more recent CP block.
Also, some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.

\end{definition}

Note that the ``closest CP blocks'' property must also apply to agreed enclosure. 
Suppose a chain is in the form
$\{c_{i}, c_{i+1}, t_{i+2}, c_{i+3}\}$\footnote{Usually the notation is of the form $c_{u, i}$, but the node identity is not important here so we simplify it to $c_{i}$}
and $c_{i}, c_{i+1}, c_{i+3}$ are in $\C_r, \C_{r+1}, \C_{r+3}$ respectively,
then the agreed enclosure of $t_{i+2}$ is $\langle c_{i+1}, c_{i+3}\rangle$ and cannot be $\langle c_{i}, c_{i+3}\rangle$.

@@

\subsection{Consensus Protocol}
\subsubsection{Bootstrap phase}
\label{sec:bootstrap}
Now we have all the necessary information to describe our consensus protocol.
As with all distributed systems, there must be a bootstrap phase which sets up the system.

The reader may notice from the system overview (\Cref{sec:system-overview}) that the facilitators are computed from the consensus result,
but the consensus result is agreed by the facilitators.
Thus we have a dependency cycle.
The goal of the bootstrap phase is to give us a starting point in the cycle.

To bootstrap, imagine that there is some bootstrap oracle, that initiates the code on every node.
The code satisfies all the properties in \Cref{def:consensus}.
Namely, every node has the same set of valid facilitators $\F_1$ that are randomly chosen.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

Continuing, when $\F_{r}$ reaches agreement on $\C_{r+1}$,
they immediately broadcast two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
Recall that channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, To guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

    \If{$F_{v, j}$ is not a fragment created in the same round as $F_{u, i}$}
        \State \Return \emph{unknown}
    \EndIf
    \State

    \label{line:valid-fragment}
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf
    \State

@@

    % message tampering
    \If{$m \ne m' \vee txid \ne txid'$} 
        \State \Return \emph{invalid}
    \EndIf
    \State

@@

\subsubsection{Using epidemic protocol to reduce communication cost}
One of the final steps in our consensus protocol is to broadcast the consensus result and signatures to every other node (\Cref{sec:consensus-phase}).
While this guarantees delivery (since we assumed reliable channel), it is wasteful.
For example, if every facilitator is honest, a node would receive $n$ consensus results which are identical when only one is necessary.
Furthermore, realistic networks do not offer a broadcast primitive,
i.e. firewalls may block incoming messages from certain nodes.

An improvement is use an epidemic protocol~\cite{eugster2004epidemic} (also known as gossiping) instead of our broadcast approach.
Typical epidemic protocols works as follows.
Every node buffers every message it receives up to some buffer size $b$.
Then it forwards the messages $t$ number of times.
Every time the message is sent to $f$ random neighbours, $f$ is often called the fan-out.
The upside of using epidemic protocol is that the communication cost is distributed more evenly between nodes.
This is especially true with a lazy push approach where the node who just received a message would push the message ID (e.g. digest) to its $f$ random neighbours,
and only push the full message if the neighbour explicitly requests the message~\cite{leitao2007epidemic}.
With this, nodes typically only need to receive one consensus result message instead of $n$.

A down side of an epidemic protocol is that it usually takes $O(\log N)$ time to infect the whole network,
whereas broadcasting uses constant time.
Another downside of some epidemic protocols (e.g. eager push) is that it is difficult to guarantee delivery.
It is especially true when the parameters are not chosen correctly in a network that is only partially connected (but every node is nevertheless reachable).
If the delivery cannot be guaranteed, 
then we cannot guarantee liveness in our consensus protocol because a future facilitator may miss the memo.
Picking parameters are difficult in practice because the network configuration is unknown and the total number of nodes might also be unknown.

@@

The space saving of this approach depends on the size of the full blocks.
If the full blocks are on average 500 bytes
(which is the typical size of Bitcoin transactions ~\cite{txsize}),
and the compact blocks are $32 + 32 + 8 = 72$ bytes
(SHA256 digests are 32 bytes each and we use a 64-bit integer to represent the sequence number),
then the saving in communication cost is 86\%.

%Using compact blocks, it is possible to reduce network communication costs in the validation protocol but also protect transaction privacy.

@@

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.
The probability that an honest node catches out a malicious node is 
$$p = \frac{f}{r},$$
where $f$ is the number of bad agreed fragments and $r$ is the latest round number.
If there are more nodes (say $n$) trying to make transactions with the malicious node,
then the probability that the malicious node gets caught at least once (denoted by the random variable $X$) follows a binomial distribution, i.e.
$$\Pr[X > 0] = \sum_{k = 1}^{n}\binom{n}{k}p^k (1 - p)^{n - k}.$$

>>>>

\subsection{Overview and intuition}
Unlike most blockchain systems, we do not use a global ledger.
Instead, every node has their own hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
We introduce a special block called checkpoint (CP) block, which represents the state of a hash chain.
The data structure is called Extended TrustChain, a visualisation can be seen on~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the Extended TrustChain. $t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.}
\label{fig:trustchain-good-cp}
\end{figure}

We randomly elect special nodes called facilitators in every round.
The facilitators reach consensus on CP blocks and the consensus result is essentially a set of CP blocks of from (nearly) all the nodes.
While this gives us consensus on a representation of the global state, it does not imply consensus on transactions.
To this end, we introduce the validation protocol that allows any nodes to challenge any other node to produce a set of TX blocks that computes to the CP block in consensus.
Hence we implicitly achieve consensus on transactions.

@@

We assume purely asynchronous channels with eventual delivery.
Thus in no stage of our protocol do we make timing assumptions.
The adversary has full control of the delivery schedule and the message ordering of all messages.
But they are not allowed to drop messages except for their own\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
}.
Further, we assume there exists a Public Key Infrastructure (PKI),
and nodes are identified by their unique and permanent public key.

@@

Our consensus protocol runs in rounds.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e. $\C_r = \langle r, C \rangle$,
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

@@

If there exist a tuple $\langle c_{u,a}, c_{u, b} \rangle$ for a TX block $t_{u, i}$,
where 
$$a = \argmin_{k, k < i, \texttt{typeof}(b_{u,k}) = \gamma}(i - k)$$
$$b = \argmin_{k, k > i, \texttt{typeof}(b_{u,k}) = \gamma}(k - i),$$
then $\langle c_{u,a}, c_{u, b} \rangle$ is the enclosure of $t_{u, i}$.
Intuitively, that is the two closest CP blocks that surround $t_{u, i}$.
Note that $c_{u, a}$ is the more recent CP block.
Also, some TX blocks may not have any enclosure, then its enclosure is $\bot$.
Agreed enclosure is the same as enclosure with an extra constraint where the CP blocks must be in some consensus result $\C_r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block.
The objectives of the protocol are to
    allow honest nodes always make progress (in the form of creating new CP blocks),
    compute correct consensus result in every round
    and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

\subsubsection{Bootstrap phase}
\label{sec:bootstrap}
As with many distributed systems, there must be a bootstrap phase which sets up the system.
Imagine that there is some bootstrap oracle, that initiates the code on every node.
The code satisfies all the properties in \Cref{def:consensus}.
Namely, every node has the same set of valid facilitators $\F_1$ that are randomly chosen.
This concludes the bootstrap phase.
For any future rounds, the consensus phase is used.

@@

Continuing, when $\F_{r}$ reaches agreement on $\C_{r+1}$,
they immediately broadcast\footnote{An alternative to using broadcasting is to use an epidemic protocl~\cite{eugster2004epidemic}, 
as long as it can guarantee delivery.} two messages to all the nodes---
first the consensus message $\langle \texttt{cons\_msg}, \C_{r+1} \rangle$,
and second the signature message $\langle \texttt{cons\_sig}, r, sig \rangle$.
The reason for sending \texttt{cons\_sig} is the following.
Recall that channels are not authenticated, 
and there are no signatures in $\C_{r + 1}$.
If a non-facilitator sees some $\C_{r + 1}$, it cannot immediately trust it because it may have been forged.
Thus, To guarantee authenticity, every facilitator sends an additional message that is the signature of $\C_{r + 1}$.

@@

    \If{$F_{v, j}$ is not a fragment created in the same round as $F_{u, i}$}
        \State \Return \emph{unknown}
    \EndIf

    \label{line:valid-fragment}
    \State $\langle \_, \_, txid, pk_v, m, \_ \rangle \gets t_{u, i}$
    \If{number of blocks of $txid$ in $F_{v, j} \ne 1$}
        \State \Return \emph{invalid}
    \EndIf

@@

    % message tampering
    \If{$m \ne m' \vee txid \ne txid'$} 
        \State \Return \emph{invalid}
    \EndIf

@@

@@

@@

The second approach is probabilistic but with only a constant communication overhead over our current design.
For a node, observe that if all of its agreed fragments has a transaction with an honest node,
then the complete chain is effectively validated in a distributed manner.
The only way for an attacker to make a fork is to make sure that the agreed fragment containing the fork has no transactions with honest nodes.
Such malicious behaviour is prevented probabilistically using a challenge-response protocol as follows.
Suppose node $A$ wish to make a transaction with node $B$.
$A$ first sends a challenge to $B$ asking it to prove that it holds a valid agreed fragment between some consensus round specified by $A$.
If $B$ provides a correct proof, then they run the transaction protocol as usual.
If $B$ provides an invalid proof or refuses to respond,
then $A$ would refuse to make the transaction.

### 2017-08-09 paper/s5-evaluation.tex
Write/fix paper

\section{Experimental Evalutation}

\subsection{Communication cost of the consensus protocol}

\begin{figure}[tb]
  \centering
  \includegraphics[width=\linewidth]{neighbour-random/round-communication-cost-vs-population}
  \caption{Communication cost for the consensus protocol per round increases linearly with population size.
  The error bars are larger for higher population size or higher number of facilitators is because rounds take longer thus they are repeated fewer times.}
  \label{fig:round-comms}
\end{figure}

\begin{figure}[tb]
  \centering
  \includegraphics[width=\linewidth]{neighbour-random/round-duration-vs-population}
  \caption{Round duration does not increase linearly with the population size. 
  This is likely due to the additional hashing operation required for larger consensus result.}
  \label{fig:round-duration}
\end{figure}

\Cref{fig:round-comms} shows the relationship between the communication cost of the consensus protocol per round and the population size.
The most important aspect is that these results show a linear increase.
This reinforces our analytical result in~\Cref{sec:cons-complexity}.
Note that regardless of whether the transactions are performed with a random neighbour or with a fixed neighbour,
the magnitude of the communication cost is similar.
Both peak at about 100 MB.
This is expected because the consensus protocol is decoupled from the transaction protocol and the validation protocol.
Finally, the rate for which the communication cost increases is higher when the number of facilitators is higher.
This is also expected because the ACS algorithm has an $n^2$ term in its communication complexity.

We are also interested in how communication costs translate to time.
Hence, for the same experiment, we record the duration in seconds and the result is shown in~\Cref{fig:round-duration}.
Interestingly, the duration is not entirely linear.
We attribute this behaviour to the extra time needed to hash the CP blocks in the consensus result to compute the luck value.
Since if $N$ increases, every node must also perform more hash operations.
These results do not conform to analytical result in~\Cref{sec:cons-duration}.
Nevertheless, the difference is minor and there are ways to optimise the luck value computation.
For example, the luck value can be computed by the facilitators and are sent with the consensus result.
Then the non-facilitator nodes simply use it if there are enough signatures.

\subsection{Communication cost of transaction and validation}
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{neighbour-random/tx-communication-cost-vs-population}
  \caption{Communication cost per verified transaction has similar (near linear) trend as~\Cref{fig:round-duration}.
  Fluctuation for the fixed-neighbour mode exists because the cache mechanism is unpredictable.}
  \label{fig:tx-comms}
\end{figure}

@@

@@

Finally, the global throughput results are shown in~\Cref{fig:global-throughput}.
Evidently, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.

>>>>

\section{Implementation and Evaluation}

The prototype implementation can be found on GitHub.
\begin{displayquote}
\url{https://github.com/kc1212/consensus-thesis-code}
\end{displayquote}
It implements the three protocols and the Extended TrustChain.
We also implement two optimisations---privacy preserving validation protocol using compact blocks (\Cref{sec:compact})
and optimised validation protocol using cached agreed fragments (\Cref{sec:caching}).
It is written in the event driven paradigm, using the Python programming language\footnote{\url{https://www.python.org/}}.
The cryptography primitives we use are SHA256 for hash functions and Ed25519 for digital signatures.
Both of which are provided by libnacl~\footnote{\url{https://pypi.python.org/pypi/libnacl}}.

\subsection{Experimental setup}
\label{sec:experimental-setup}

We run the experiment on the DAS-5\footnote{\url{https://www.cs.vu.nl/das5/}} with up to 1200 nodes.
Every node makes a transaction with a random node twice every second.
Since Bitcoin transactions are approximately 500 bytes~\cite{txsize},
we use a uniformly random transaction size sampled between 400 and 600 bytes.

To coordinate nodes on many different machines,
we employ a discovery server to inform every node the IP addresses and port numbers of every other node.
It is only run before the experiment and is not used during the experiment.

@@

The global throughput results are shown in~\Cref{fig:global-throughput}.
Evidently, the throughput has a linear relationship with the population size.
This result is a strong indication of the horizontal scalability which we aimed to achieve.

@@
